\class : Problem Set \psetnum

### 2022-05-16 531_stars/pset4/solutions.tex
q1 and q2 done stars hw4

    The values of $\mu_{\rm ion}$ for these WDs are $1, 4, 12$ respectively. This means that the relative luminosity of the WDs is
    \begin{equation}
        \frac{L}{L_{\rm H-rich}} = 1 : 0.14 : 0.03
    \end{equation}
    respectively. This shows that H-rich WDs are the brightest for a given cooling age, following my He-rich and then C-rich WDs.

    \todo{Can we assume that the mass is constant?}
}

\question{Part b - Reason for differences}
\answer{
    \todo{Unsure, maybe larger ions make cooling happen faster? Why?}
}

\question{\textbf{23.2 - Central Temperature-Density Gradient}}
\answer{
    The evolution of a star in the $T_c$--$\rho_c$ diagram becomes less steep at late evolution phases. This means that for a given increase in density, the increase in temperature is not as strong.
    \todo{I think this is probably something to do with the mass defect being lower and so the energy/temperature production is lower?}
}

\clearpage

>>>>

    The values of $\mu_{\rm ion}$ for these WDs are $1, 4, 12$ respectively. This means that the relative luminosity of the WDs is
    \begin{equation}
        \frac{L}{L_{\rm H-rich}} = 1 : 0.14 : 0.03
    \end{equation}
    respectively. This shows that H-rich WDs are the brightest for a given cooling age, following my He-rich and then C-rich WDs.
}

\question{Part b - Reason for differences}
\answer{
    The cooling of a WD is due to the loss of the thermal energy of the ions. The specific heat of a substance gives a measure for how much energy is required to change its temperature by a given amount. Therefore, a smaller specific heat means that cooling an object is easier and will happen more quickly. The specific heat of the ion is given by
    \begin{equation}
        c_V = \frac{3 k}{2 m_{\rm ion}}
    \end{equation}
    This means that for helium and carbon, the increased $m_{\rm ion}$ results in a smaller specific heat and thus faster cooling rate.
}

\question{\textbf{23.2 - Central Temperature-Density Gradient}}
\answer{
    For most of its life the star follows
    \begin{equation}
        T_c \sim \rho_c^{1/3},
    \end{equation}
    however this trend becomes less steep over time. This is because the full expression is actually
    \begin{equation}
        T_c \sim M_c^{2/3} \rho_c^{1/3},
    \end{equation}
    For the later fusion phases, the core mass becomes much lower (see Eq.\ 14.10) and so we can't assume it to be constant. Therefore, we see that for late fusion phases the increase in temperature for a given density is lower, thus the evolution in the plot is less steep.
}
